%% ===========================================================================
%% TITLE PAGE (with author details) — submit as a SEPARATE file from the
%% anonymized manuscript (Information Processing & Management uses double-
%% anonymized review). Fill in the [[...]] placeholders before submission.
%% ===========================================================================
\documentclass[preprint,12pt]{elsarticle}
\usepackage{amssymb,amsmath}
\journal{Information Processing \& Management}

\begin{document}

\begin{frontmatter}

\title{Popularity Bias and Cold-Start in Patent Technology-Transfer
Demand Prediction: A Diagnostic Evaluation}

%% --- Authors (match the order in the submission system; check spelling) ---
\author[hyis]{Sangwon Lee}
\author[hyme]{Kyungseok Lee\corref{cor1}}
\ead{bu5119@hanyang.ac.kr}
\author[hyme]{Jaewon Lee}
\author[lg]{Dongkyu Lee\corref{cor2}}
\ead{dongkyu44.lee@lge.com} %% [[confirm Dongkyu Lee's email]]

\affiliation[hyis]{organization={Division of International Studies, Hanyang University},
            city={Seoul},
            postcode={04763},
            country={Republic of Korea}}

\affiliation[hyme]{organization={School of Mechanical Engineering, Hanyang University},
            city={Seoul},
            postcode={04763},
            country={Republic of Korea}}

\affiliation[lg]{organization={Quantum AI Task, LG AI Lab, CTO Division, LG Electronics Co., Ltd.},
            addressline={19 Yangjae-daero 11-gil, Seocho-gu},
            city={Seoul},
            postcode={06772},
            country={Republic of Korea}}

\cortext[cor1]{Corresponding author.}
\cortext[cor2]{Corresponding author.}

\begin{abstract}
(The abstract is included in the anonymized manuscript file; it may be repeated
here or omitted on the title page per the editor's preference.)
\end{abstract}

\begin{keyword}
patent technology transfer \sep link prediction \sep graph neural networks \sep
popularity bias \sep cold-start \sep evaluation methodology
\end{keyword}

\end{frontmatter}

%% ===========================================================================
\section*{CRediT authorship contribution statement}
%% Edit to reflect actual contributions; remove roles that do not apply.
\textbf{Sangwon Lee:} Investigation, Data curation, Visualization,
Writing -- original draft.
\textbf{Kyungseok Lee:} Conceptualization, Methodology, Software, Formal analysis,
Writing -- original draft, Writing -- review \& editing.
\textbf{Jaewon Lee:} Software, Validation, Investigation.
\textbf{Dongkyu Lee:} Conceptualization, Supervision, Funding acquisition,
Writing -- review \& editing.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or
personal relationships that could have appeared to influence the work reported in
this paper.

\section*{Declaration of generative AI and AI-assisted technologies in the writing process}
During the preparation of this work the authors used Claude (Anthropic) in order to
improve the language, grammar, and readability of the manuscript. After using this
tool, the authors reviewed and edited the content as needed and take full
responsibility for the content of the publication.

\section*{Funding}
This research did not receive any specific grant from funding agencies in the public,
commercial, or not-for-profit sectors.

\section*{Acknowledgements}
%% Optional: language/writing help, computing resources, helpful discussions.
%% (Funding is declared above; do NOT place acknowledgements in the anonymized
%%  manuscript or as a footnote to the title.)
[[Optional --- add any non-funding acknowledgements (e.g., helpful discussions), or
remove this section.]]

\section*{Data availability}
The patent data were obtained from the Korea Intellectual Property Rights Information
Service (KIPRIS) through its paid API (KIPRIS Plus, https://plus.kipris.or.kr) and
were subsequently cleaned and processed by the authors. Because redistribution of
these data is restricted by the KIPRIS terms of use, the processed dataset is not
deposited in a public repository; it is instead available from the corresponding
author by email upon reasonable request, subject to those terms. The preprocessing and
evaluation code, experiment scripts, and an embedding-regeneration script are released
at [[repository URL / DOI]], enabling full reproduction of all tables and figures.

\end{document}
